Final Project Data 205

### 2021-12-07 Draft Final Project1.Rmd
Add files via upload

url <- "https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-"
time_periods <- c("October-2021","September-2021", "August-2021", "July-2021", "June-2021","May-2021","April-2021","March-2021","February-2021","January-2021","December-2020","November-2020","October-2020","September-2020","August-2020","May-2020","April-2020","March-2020","February-2020","January-2020","December-2019","November-2019","October-2019","June-2019","November-2018")

@@

url_exception_july_2019<-"https://www.wmata.com/about/transit-police/upload/July-2019-Blotter.pdf"
df_exception_July_2019 <- get_wmata_data(url_exception_July_2019)

url_exception_may_2019<-"https://www.wmata.com/about/transit-police/upload/May-2019-Blotter-Report.pdf"
df_exception_May_2019 <- get_wmata_data(url_exception_May_2019)

url_exception_april_2019<-"https://www.wmata.com/about/transit-police/upload/Blotter-Report-April-2019.pdf"
df_exception_April_2019 <- get_wmata_data(url_exception_April_2019)

url_exception_march_2019<-"https://www.wmata.com/about/transit-police/upload/2019-March-Blotter-Report.pdf"
df_exception_March_2019 <- get_wmata_data(url_exception_March_2019)

url_exception_february_2019<-"https://www.wmata.com/about/transit-police/upload/February-2019-Monthly-Blotter-Report.pdf"
df_exception_February_2019 <- get_wmata_data(url_exception_February_2019)

url_exception_january_2019<-"https://www.wmata.com/about/transit-police/upload/January-2019-Monthly-Blotter-Report.pdf"
df_exception_January_2019 <- get_wmata_data(url_exception_January_2019)

url_exception_december_2018<-"https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-2018-December.pdf"
df_exception_December_2018 <- get_wmata_data(url_exception_December_2018)

url_exception_october_2018<-"https://www.wmata.com/about/transit-police/upload/October-2018-Monthly-Crime-Blotter.pdf"
df_exception_October_2018 <- get_wmata_data(url_exception_October_2018)

url_exception_september_2018<-"https://www.wmata.com/about/transit-police/upload/September-2018-Blotter.pdf"
df_exception_September_2018 <- get_wmata_data(url_exception_September_2018)

url_exception_august_2018<-"https://www.wmata.com/about/transit-police/upload/August-2018-Monthly-Blotter.pdf"
df_exception_August_2018 <- get_wmata_data(url_exception_August_2018)

@@

  if (df_prev == "")
  {
    df_prev <- df_curr
    df_wmata <- df_prev
  } else {
    df_wmata <- bind_rows(df_wmata, df_curr,url_exception_june_2020,url_exception_june_2020,url_exception_march_2019,url_exception_february_2019,url_exception_january_2019,url_exception_december_2018,url_exception_october_2018,url_exception_september_2018,url_exception_august_2018)
  }
}

@@

@@

```{r}

@@

>>>>

url <- "https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-"
time_periods <- c("October-2021","September-2021", "August-2021", "July-2021", "June-2021","May-2021","April-2021","March-2021","February-2021","January-2021","December-2020","November-2020","October-2020","September-2020","August-2020","May-2020","April-2020","March-2020","February-2020","January-2020","December-2019","November-2019","October-2019","June-2019","November-2018","March-2018","February-2018","January-2018","October-2017","September-2017")

@@

url_exception_september_2019<-"https://www.wmata.com/about/transit-police/upload/September-2019-Monthly-Blotter.pdf"
df_exception_September_2019 <- get_wmata_data(url_exception_september_2019)

url_exception_august_2019<-"https://www.wmata.com/about/transit-police/upload/August-2019-Monthly-Blotter.pdf"
df_exception_August_2019 <- get_wmata_data(url_exception_august_2019)

url_exception_july_2019<-"https://www.wmata.com/about/transit-police/upload/July-2019-Blotter.pdf"
df_exception_July_2019 <- get_wmata_data(url_exception_july_2019)

url_exception_may_2019<-"https://www.wmata.com/about/transit-police/upload/May-2019-Blotter-Report.pdf"
df_exception_May_2019 <- get_wmata_data(url_exception_may_2019)

url_exception_april_2019<-"https://www.wmata.com/about/transit-police/upload/Blotter-Report-April-2019.pdf"
df_exception_April_2019 <- get_wmata_data(url_exception_april_2019)

url_exception_march_2019<-"https://www.wmata.com/about/transit-police/upload/2019-March-Blotter-Report.pdf"
df_exception_March_2019 <- get_wmata_data(url_exception_march_2019)

url_exception_february_2019<-"https://www.wmata.com/about/transit-police/upload/February-2019-Monthly-Blotter-Report.pdf"
df_exception_February_2019 <- get_wmata_data(url_exception_february_2019)

url_exception_january_2019<-"https://www.wmata.com/about/transit-police/upload/January-2019-Monthly-Blotter-Report.pdf"
df_exception_January_2019 <- get_wmata_data(url_exception_january_2019)

url_exception_december_2018<-"https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-2018-December.pdf"
df_exception_December_2018 <- get_wmata_data(url_exception_december_2018)

url_exception_september_2018<-"https://www.wmata.com/about/transit-police/upload/September-2018-Blotter.pdf"
df_exception_September_2018 <- get_wmata_data(url_exception_september_2018)

url_exception_august_2018<-"https://www.wmata.com/about/transit-police/upload/August-2018-Monthly-Blotter.pdf"
df_exception_August_2018 <- get_wmata_data(url_exception_august_2018)

url_exception_july_2018<-"https://www.wmata.com/about/transit-police/upload/July-2018-Blotter.pdf"
df_exception_July_2018 <- get_wmata_data(url_exception_july_2018)

url_exception_june_2018<-"https://www.wmata.com/about/transit-police/upload/June-2016-Blotter.pdf"
df_exception_June_2018 <- get_wmata_data(url_exception_june_2018)

url_exception_may_2018<-"https://www.wmata.com/about/transit-police/upload/May-Monthly-blotter-2018.pdf"
df_exception_May_2018 <- get_wmata_data(url_exception_may_2018)

url_exception_april_2018<-"https://www.wmata.com/about/transit-police/upload/April-Monthly-blotter.pdf"
df_exception_April_2018 <- get_wmata_data(url_exception_april_2018)

url_exception_december_2017<-"https://www.wmata.com/about/transit-police/upload/December-Monthly-Blotter.pdf"
df_exception_December_2017 <- get_wmata_data(url_exception_december_2017)

url_exception_november_2017<-"https://www.wmata.com/about/transit-police/upload/November-Monthly-Blotter.pdf"
df_exception_November_2017 <- get_wmata_data(url_exception_november_2017)

url_exception_august_2017<-"https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-Report-August-2017.pdf"
df_exception_August_2017 <- get_wmata_data(url_exception_august_2017)

url_exception_july_2017<-"https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-Report-July-2017.pdf"
df_exception_July_2017 <- get_wmata_data(url_exception_july_2017)

url_exception_june_2017<-"https://www.wmata.com/about/transit-police/upload/June-2017-blotter.pdf"
df_exception_June_2017 <- get_wmata_data(url_exception_june_2017)

url_exception_april_2017<-"https://www.wmata.com/about/transit-police/upload/April-2017-monthly-blotter.pdf"
df_exception_April_2017 <-get_wmata_data(url_exception_april_2017)

url_exception_march_2017<-"https://www.wmata.com/about/transit-police/upload/March-2017-monthly-blotter.pdf"
df_exception_March_2017 <-get_wmata_data(url_exception_march_2017)

url_exception_february_2017<-"https://www.wmata.com/about/transit-police/upload/January-2017-monthly-blotter.pdf"
df_exception_February_2017 <-get_wmata_data(url_exception_february_2017)

url_exception_january_2017<-"https://www.wmata.com/about/transit-police/upload/Monthly-Blotter_February-2017.pdf"
df_exception_January_2017 <-get_wmata_data(url_exception_january_2017)

@@

  if (df_prev == "")
  {
    df_prev <- df_curr
    df_wmata <- df_prev
  } else {
    df_wmata <- bind_rows(df_wmata,df_curr,df_exception_June_2020,df_exception_July_2020,df_exception_September_2019,df_exception_August_2019,df_exception_March_2019,df_exception_February_2019,df_exception_January_2019,df_exception_December_2018,df_exception_September_2018,df_exception_August_2018,df_exception_July_2018, df_exception_June_2018,df_exception_May_2018,df_exception_April_2018,df_exception_December_2017,df_exception_November_2017,df_exception_August_2017,df_exception_July_2017,df_exception_June_2017,df_exception_April_2017,df_exception_March_2017,df_exception_February_2017,df_exception_January_2017)

  }
}

@@

```
## View df_wmata Data 
```{r}
view(df_wmata)
```

## Summary
```{r}
summary(df_wmata)
```

## Get rid of NAs
```{r}
WMATA <-na.omit(df_wmata)
```

## 
```{r}
tuition$tuition$name[grepl('State University of New York', tuition$name)] <- 
```

## Two links that will not load & has an error
```{r}

url_exception_october_2018<-"https://www.wmata.com/about/transit-police/upload/October-2018-Monthly-Crime-Blotter.pdf"
df_exception_October_2018 <- get_wmata_data(url_exception_october_2018)

url_exception_may_2017<-"https://www.wmata.com/about/transit-police/upload/May-2017-Blotter.pdf"
df_exception_May_2017 <- get_wmata_data(url_exception_may_2017)

@@

```{r}
,url_exception_june_2020,url_exception_july_2020,url_exception_september_2019,url_exception_august_2019,url_exception_july_2019,url_exception_march_2019,url_exception_february_2019,url_exception_january_2019,url_exception_december_2018,url_exception_september_2018,url_exception_august_2018,url_exception_july_2018,url_exception_june_2018,url_exception_may_2018,url_exception_april_2018,url_exception_december_2017,url_exception_november_2017,url_exception_june_2017,url_exception_april_2017,url_exception_march_2017,url_exception_january_2017
```

@@

## Remove Crimes Data 
```{r}
na.omit(crimes)
```

```{r}
view(crimes)
```

```{r}
names(crimes)[names(crimes) == 'Crime Name1'] <- 'Offenses'
```

```{r}
P1<-crimes %>%                        
  group_by(type) %>% 
  select("")
  summarize(n = n())
P1
```

```{r}
ggplot(crimes, aes(x=Offenses, fill=Offenses)) + 
  geom_bar( ) +
  scale_fill_hue(c = 40) +
  theme(legend.position="none")
```
